### 2023-03-23 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny

The multicomponet vesicle satisfies the no-slip boundary condition
$\frac{d\xx}{dt} = \uu(\xx)$, where $\xx(s,t)$ is the arclength
parameterization of $\gamma$. Along the solid wall $\Gamma$, we impose a
Dirichlet boundary condition $\uu(\xx) = \UU(\xx)$, where $\UU$ is a
Hagen–Poiseuille flow at the inlet and outlet,
\begin{align}
  \UU(\xx) = \chi \left(1 - \left(\frac{y}{W}\right)^2 \right), 
    \quad \xx = (x,y) \in \Gamma,
\end{align}
and $\UU$ is zero along the top and bottom of the channel.

>>>>

On the multicomponet vesicle $\gamma$ the velocity satisfies the no-slip boundary condition
$\frac{d\xx}{dt} = \uu(\xx)$, where $\xx(s,t)$ is the arclength
parameterization of $\gamma$. Along the solid wall $\Gamma$, we impose a
Dirichlet boundary condition $\uu(\xx) = \UU(\xx)$, where $\UU$ is a
Hagen–Poiseuille flow at the inlet and outlet (where $y\in[-W,W]$),
\begin{align}
  \UU(\xx) = \chi \left(1 - \left(\frac{y}{W}\right)^2 \right), 
    \quad \xx = (x,y) \in \Gamma,
\end{align}
and $\UU$ is zero along the top and bottom of the channel.
